---
title: "Task 2" 
subtitle: "Wax On, Wax off"
author: "Kyle Tolliver"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_libraries, include=FALSE}
#All Library Includes

library(nycflights13) #Analysis Flights
library(dplyr)        #Gives different ways to analysis values
library(knitr)
library(ggplot2)
library(tidyverse)
library(readr)
```

## Background
This task is intended to get all of us on the same page in R. You will copy code from your readings and then improve the Research and Creative Works conference visulization from this Excel file. Even if you have used R before, this will be an excellent refresher. If you do not get the title of this task, watch this.

## Readings
* Chapter 4: R for Data Scientists - Workflow Basics
* Modern Drive: Chapter 1 Getting Started with Data in R
* Using the geom_col function
* Using the geom_line function

## Tasks
[X] Make an R script that has the code examples from Chapter 4 of R for data science and Chapter 1 of Modern Drive 

* [X] Write a short comment in your R script that explains 1-2 new concepts you learned about R

Chapter 4 -- R for data science
```{r}
#Examples
1 / 200 * 30
(59 + 73 + 2) / 3
sin(pi / 2)
x <- 3 * 4
x
x <- "hello world" #This is how to output 
x                  #things in variables
x <- "hello" #Assignments are different then other programming languages  
x
y <- seq(1, 10, length.out = 5)
y
(y <- seq(1, 10, length.out = 5))
#Practice
my_variable <- 10
my_varıable
```
```{r}
#Fix This Code
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))
 
 filter(mpg, cyl == 8)
 filter(diamonds, carat > 3)
```
Chapter 1 -- Modern Drive
```{r}
#Examples
2 + 1 == 3 #Comparator operations
4 + 2 >= 3
3 + 5 <= 1
(2 + 1 == 3) & (2 + 1 == 4)
(2 + 1 == 3) | (2 + 1 == 4)
seq(from = 1, to = 1)
seq(from = 2, to = 5)
flights
View(flights)
glimpse(flights)
airlines
kable(airlines)
airlines$name
glimpse(airports)
```

[X] Improve the 3D barchart visuallization using R (code below) to provide a graphic that answers the question, What is the trend by department of RC&W attendance? (data and 3D visualization) ---
library(tidyverse)
dat <- read_csv("https://byuistats.github.io/M335/data/rcw.csv")

```{r, fig.height=6, fig.width=8}
theme_update(plot.title = element_text(hjust = 0.5))
dat <- read_csv("https://byuistats.github.io/M335/data/rcw.csv")

dat %>%
  mutate(Year2 = Year %>% as.character(Year)) %>% 
  unite("Semester_Year", Semester, Year2, remove = FALSE) %>%
  mutate(Semester_Year = Semester_Year %>% 
           factor(level = c("Spring_2016", "Fall_2016", "Winter_2017", "Spring_2017", "Fall_2017", "Winter_2018"))) %>%
ggplot() +
  geom_point(mapping = aes(x = Department, y = Count, color = Semester_Year)) +
  labs(color = "Semester", 
       title = "Research and Creative Works Conference")
```

[X] Create a GitHub account --- https://github.com/kctolli

* [X] Post your github username on the google docs sheet --- kctolli
* [X] Post a professional picture to your Github, LinkedIn, and Slack icons. Go to the BYU-I LinkedIn Photobooth if you don’t already have one.

[X] Attend Data Science Society on the second Wednesday of the semester. 

* 6pm in STC 385 

## Class Notes

### Effectively Communicating Numbers

1. Message
2. Graphics
3. Data Munging
4. Fine the Message
5. Clarify the point 

### Asking the Right Questions

* Harness the power of questions and Clarify Terms
* A truly wise person may not have the answers, but know which questions to ask

### Three Traits of a Data Scientist

1. Ask questions that matter?

* What does that mean?

2. Determine the question has been answered.

* Identify and satisfy assumptions
* A commitment to intellectual honesty
* What does that mean?

3. Creative thinking

* Vigorous attempts to fail their own answers?

An easy way to assess job candidates on the three traits is to ask them to briefly describe one or more of their past projects, and then ask them many follow-up questions about whether and how they applied the three traits.

### HotKeys

* %>% -- ctrl shift m
* comments -- ctrl shift c
* hotkeys -- shift alt k

