---
title: "Kyle Tolliver"
---

```{r load_libraries, include=FALSE}
library(tidyverse)
```

```{r pic, fig.align='left', out.width='30%', echo = FALSE}
me <- './site_libs/images/me.png'
knitr::include_graphics(me)
```

## About Me

BYU-Idaho Senior studying Software Engineering and Data Science. Expected graduation in December of 2020. I enjoy several different disciplines in software engineering. I am also working toward a Computer Engineering minor. I love to learn new things and solve problems.

## Contact Me

Email: kyle@tollivers.org

Phone: [(805) 367-6723](tel:18053676723)

<br /> <br />

## Posts

* [Data Science Coursework](./Data-Science/index.html)
* [COVID-19 Research and Consulting](https://kctolli.github.io/COVID-19/index.html)
* [Useful R Package](https://github.com/kctolli/Useful-R)
* [Web Design and Development](https://wdd-100-dry.glitch.me/)
* [Digital System Design Coursework](https://ecen-340.glitch.me/)
* [Senior Design Project](https://ecen499-nasa.github.io/)
* [Current-limited DC Power Supply](./site_libs/ECEN350-report.pdf)

<br /> <br />

© Copyright Kyle Tolliver, 2020

###### *--- [Licensed](https://github.com/kctolli/kctolli.github.io/blob/master/LICENSE) under [GNU General Public License v3.0](./site_libs/LICENSE.txt)*

######  *--- Website is made with [Rmd files](https://rmarkdown.rstudio.com/index.html) and [Rstudio](https://rstudio.com/)*

######  *--- Hosted on [github](https://github.com/kctolli/kctolli.github.io)*

