---
title: "Program of Study"
editor_options: 
  chunk_output_type: console
---

```{r load_libraries, include=FALSE}
source("./site_libs/site.R")
file <- "pos"
```

`r nav()`

## Brigham Young University - Idaho

I earned a Bachelor's of Science in Software Engineering <br />with a minor in Computer Engineering and Data Science.

<div `r px0()`><span class="tooltipr"><a href="javascript:showhide('diploma')">Diploma</a>
<span class="tooltipRtext">`r print_strong("2020 Graduate")`<br/>My cumulative GPA was <br/> 3.6 out of 4</span></span>
<div id="diploma" align="center" `r px20()`>`r print_pic("./site_libs/images/diploma.jpg")`</div></div>

```{r BYUI}
print_newline()
print_h3("Software Engineering (BS)")
print_pos('SE')
print_newline()
print_h3("Computer Engineering Minor")
print_pos('CE')
print_newline()
print_h3("Data Science Minor")
print_pos('DS')
print_newline()
print_h3("Core {.tabset .tabset-fade}")
print_h4("Programming")
print_pos('GP')
print_newline()
print_h4("Math and Science")
print_pos('GMS')
print_newline()
print_h4("General")
print_pos('GE')
```

## Moorpark High School

<div `r px0()`><span class="tooltipr"><a href="javascript:showhide('hs')">I was able to take some 
advanced and college level courses in the process of getting my High School Diploma.</a>
<span class="tooltipRtext">`r print_strong("2017 Graduate")`</span></span><div id="hs" `r px20()`>

```{r HS}
print_pos('HS')
```

</div></div>

```{r Self}
pagebreak()
print_h2("Solo Learn")
pander("Certificates Include: \n\n")
print_newline()
print_solo()
print_newline()
footer(file)
```
