---
title: "Program of Study"
---

```{r load, include=FALSE}
library(mosaic)
library(tidyverse)
library(pander)
library(DT) 
library(knitr)

grade <- read_csv("./site_libs/records/grade.csv") %>% na.omit()
```

<script type="text/javascript">
 function showhide(id) {
    var e = document.getElementById(id);
    e.style.display = (e.style.display == 'block') ? 'none' : 'block';
 }
</script>

<style>

</style>

## Brigham Young University - Idaho

I am senior at BYU-Idaho, with an expected graduation date of December, 2020. <br/> 
I am studying to get my Bachelor's of Science in Software Engineering with a minor in Computer Engineering. <br/> 
I am also working towards an Applied Associates of Science in Data Science.

<div style="padding-left:5px;">

<span class="tooltipr">
<a href="javascript:showhide('hovertobegin')"><p style="color:blue;">Grades</p></a>
  <span class="tooltipRtext">My cumulative GPA is 3.66 out of 4 </span>
</span>
<div id="hovertobegin" style="display:none;padding-left:20px;">

```{r display, echo=FALSE}
pander(grade, caption = "Applicable Coursework - Grades")
```

</div>
</div>

### Software Engineering (BS)

* Intro to Software Development using C++
* Object-Oriented Development using C++
* Software Design and Development using Java
* Introduction to Programming for IT
* System Security 
<!-- * JavaScript Language  -->
* Senior Practicum 
* Senior Project 

### Data Science (AAS)

* Database Design and Development
* Data Intuition and Insight
* Data Wrangling and Visualization
<!-- * Machine Learning and Data Mining -->
<!-- * Statistical Consulting -->

### Computer Engineering Minor

* Electric Circuit Analysis 
* Electronic Devices and Circuits
* Microprocessor Based-System Design
* Digital System Design
* Computer Architecture
* Embedded Systems
* Advanced Embedded Systems

### Core

#### Math and Science

* PreCalculus
* Differential Calculus
* Linear Algebra 
* Discrete Math 
<!-- * Intermediate Statistics  -->
* Introduction to Chemistry
* Foundations of Science

#### Programming

* Intro to Computer Science and Engineering
* Intro to Programming using Python
* Object-Oriented Programming with Data Structures using Python
* Introduction to Databases using SQL
* Fundamentals of Digital Systems with Lab
* Web Design and Development
* Project Management

#### General

* Family and Human Relations
* Introduction to the Visual Arts and Design
* Writing and Reasoning
* Technical Communication

## Moorpark High School

I was able to take some college level courses in the process of getting my High School Diploma. <br/> 
Moorpark High School graduating class of 2017.  

* Geometry Honors
* Algebra 2 Accelerated 
* PreCalculus Honors
* AP Calculus
* AP Chemistry
* AP Physics 1 & 2
* AP Art 2-D Design (Photography)
* Introduction to Computer Science using C++
* Introduction to Engineering
