---
title: "Projects"
---

```{r load_libraries, include=FALSE}
library(tidyverse)
library(knitr)
```

## Self Driving Car      

```{r}
car <- './images/car.jpg'
car_circuit <- './images/car_cir.jpg'
```

```{r Car1, fig.align='center', out.width='25%'}
include_graphics(car)
```

```{r Car2, fig.align='center', out.width='25%'}
include_graphics(car_circuit)
```

Spent 30 Hours on the project  

* Designed Circuits and Assembled the Electronics
*	Programmed the Arduino in Embedded C
*	Setup Raspberry Pi for Deep Learning and Computer Vision

## Calendaring App		

Spent 40 Hours on the project   

*	Used Github to develop the Java code while working with a Team 
*	Presented to the Eastern Idaho Innovator's Challenge
* See [Github for code](https://github.com/natgrimm/GitTest)

## Biology Exam Data Analysis 		

Spent 20 Hours on the project    

*	Used R and the Tidyverse package to wrangle and visualize data
*	Allowed Professors to help Improve Curriculum  
* See [Exam Data Webpage](https://mcs335.glitch.me/Semester_project.html)

## Current-limited (BJT and OP-AMP) DC Power Supply		

```{r PSU, fig.align='center', out.width='75%'}
psu <- './images/circuit.png'
include_graphics(psu)
```

Spent 20 Hours on the project   

* Calculated the value of components of the power supply
* Designed a power supply that convert 20V AC/DC to 5V DC
* Soldered the Circuit together

## FPGA (Verilog) Multifunction Calculator

Spent 30 Hours on the project 

* Created new AVR commands 
* Used Basys 3 (Artix 7) FPGA Board
* See [Multifunction Calculator Webpage](https://ecen-340.glitch.me/final-project.html)

## Electric Skateboard                          		

```{r skate, fig.align='center', out.width='50%'}
skate <- './images/skateboard.jpg'
include_graphics(skate)
```

Spent 40 Hours on the project

* Selected and assembled the components 
* Programmed the VESC in Embedded C
* Setup a Wii remote as the skateboard controller

## Optimizing Calendar C++ Program		

Spent 15 Hours on the project  

* Hyperthreaded and Pipelined a C++ Calendar 
  + Used Tomohiko Sakamoto's Algorithm 
    - To adjust for leap year 
    - To find the day of the week
* Spead up the program by about 25 times
  + About a 150 ms run time
  
## ePortfolio

Spent 10 Hours on the project - On going


* This is one place to show:
  + About Me
  + Skills
  + Program of Study
  + Projects
  + Resume
  + LinkedIn
* Hosted on [github](https://github.com/kctolli/kctolli.github.io)
  + [This website](https://kctolli.github.io/index.html)
* Used Rmd and YML files to create

## PolarFire Design Project

This project is on going 

* Sponsored by NASA
* Done in VHDL
* Implement RISC-V core on the PolarFire dev kit

## COVID-19 Analytics

This project is on going 
  