---
title: "Projects"
---

```{r load_libraries, include=FALSE}
library(tidyverse)
library(knitr)
```

## COVID-19 Analytics

2020 -- Over 165 hours 

Senior Thesis/Practicum

* Developed a data website using R, Rmds and Yaml
* Explored different datasets to determine viable information
* Wrote my own COVID-19 R package to wrangle data
* Visualized the data to make the data easily understood
* See [COVID-19 Website](https://kctolli.github.io/COVID-19/)

## Biology Exam Data Analysis 		

2020 -- Spent 20 Hours on the project   

*	Used R and the [Tidyverse package](https://tidyverse.tidyverse.org/) to wrangle and visualize data
*	Allowed professors to help improve curriculum  
* See [Exam Data Webpage](https://kctolli.github.io/MATH335/Semester_project.html)

## Self Driving Car      

2020 -- Spent 30 Hours on the project 

```{r, echo = FALSE}
car <- './site_libs/images/car.jpg'
car_circuit <- './site_libs/images/car_cir.jpg'
```

```{r Car1, fig.align='center', out.width='25%', echo = FALSE}
include_graphics(car)
```

```{r Car2, fig.align='center', out.width='25%', echo = FALSE, eval=FALSE}
include_graphics(car_circuit)
```

* Designed Circuits and Assembled the Electronics
*	Programmed the Arduino in Embedded C
*	Setup Raspberry Pi for Deep Learning and Computer Vision

## Current-limited (BJT and OP-AMP) DC Power Supply		

2019 -- Spent 20 Hours on the project

```{r PSU, fig.align='center', out.width='75%', echo = FALSE}
psu <- './site_libs/images/circuit.png'
include_graphics(psu)
```

* Calculated the value of components of the power supply
* Designed a power supply that convert 20V AC/DC to 5V DC
* Soldered the circuit together
* See [Final Project Report](./site_libs/images/ECEN350-report.pdf)

## Project Life

2019 -- Spent 10 Hours on the project 

* Used Trello (Kanban board) to plan life goals 
* Broke goals into time segments 
* Followed Agile methodology

## FPGA (Verilog) Multifunction Calculator

2019 -- Spent 30 Hours on the project 

* Created new AVR commands 
* Used Basys 3 (Artix 7) FPGA Board
* See [Multifunction Calculator Webpage](https://ecen-340.glitch.me/final-project.html)

## Optimizing Calendar C++ Program		

2019 -- Spent 15 Hours on the project  

* Hyperthreaded and Pipelined a C++ Calendar 
  + Used Tomohiko Sakamoto's Algorithm 
    - To adjust for leap year 
    - To find the day of the week
* Spead up the program by about 25 times
  + About a 150 ms run time

## Electric Skateboard                          		

2018 -- Spent 40 Hours on the project

```{r skate, fig.align='center', out.width='40%', echo = FALSE}
skate <- './site_libs/images/skateboard.jpg'
include_graphics(skate)
```

* Selected and assembled the components 
* Programmed the VESC in Embedded C
* Setup a Wii remote as the skateboard controller

## Calendaring App		

2018 -- Spent 40 Hours on the project  

*	Used Github to develop the Java code while working with a Team 
*	Presented to the Eastern Idaho Innovator's Challenge
* See [Github for code](https://github.com/natgrimm/GitTest)

## Obstacle Avoiding Car

2018 -- Spent 30 Hours on the project 

* Designed and assembled electronics
* Programmed MSP 432 using Register-level C
* Developed a working prototype

## Asteroids Game 

2017-2018 -- Spent 40 Hours on the project 

* Used C++ and Python to recreate this [classic game](https://arcade.ly/games/asteroids/)
* Created and followed a UML class Diagram
* Added additional features and graphics 
  Such as:
    + Made a Thor themed game
    + Added machine gun mode
    
## 4-Bit Microprocessor

2017 -- Spent 30 Hours on the project

* Created in both Verilog and simulation tools
* Development required many different components
  + Binary Counter 
  + Two Read Only Memories (ROM)    
  + Multiplexer (MUX) 
  + Register File
  + Arithmetic Logic Unit (ALU)
  + ASCII display
* Wrote Machine code on the ROMs to control the CPU  
  
## Toolbox Power Supply

2017 -- Spent 30 Hours on the project

* Selected and Assembled the electronics
* Wired both AC and DC electronics 
* Designed a method to convert voltages
  + 120V AC to 12V DC and 5V DC
