---
title: "Skills"
---

<!--
This program is free software: you can redistribute it and/or modify
it under the terms of the GNU General Public License as published by
the Free Software Foundation, either version 3 of the License, or
(at your option) any later version.

This program is distributed in the hope that it will be useful,
but WITHOUT ANY WARRANTY; without even the implied warranty of
MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
GNU General Public License for more details.

You should have received a copy of the GNU General Public License
along with this program.  If not, see <https://www.gnu.org/licenses/>.
-->

```{r load_libraries, include=FALSE}
source("./site_libs/script.R")
datapath <- "./site_libs/data/"
load_libraries()
```

```{r eval=FALSE}
setwd(glue("{here}kctolli.github.io/"))
render_all()
```

<script src="./site_libs/script.js"></script>

## Computer Engineering

### Embedded Systems {.tabset .tabset-fade}

#### Technologies

##### Programming

<ul>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('C')"><li style="color:gray;">C/C++</li></a>
<span class="tooltipRtext"><ul style="color:white;">
<li>Embedded</li>
<li>Register-level</li>
</ul></span></span></div>

<li>Python</li>
<li>Simulink</li>

</ul>

##### Embedded OS

<ul>

<li>ROS (Robot Operating System)</li>
<li>VxWorks</li>
<li>FreeRTOS</li>
<li>Windows IOT</li>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('linux')"><li style="color:gray;">Linux</li></a>
<span class="tooltipRtext"><ul style="color:white;">
<li>Real-Time</li>
<li>Embedded</li>
<li>Raspberry OS</li>
</ul></span></span></div>
</ul>

#### Tools

##### Environments
  
* Code Composer Studio
* SoftConsole
* MATLAB
* Energia
* Arduino IDE
  
##### Microcontrollers

* Intel Galileo
* Raspberry Pi
* LattePanda
* ESP 8266
* MSP 432
* Arduino

#### Data Transfer

##### Communication Protocols

<ul>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('uart)"><li style="color:gray;">UART</li></a>
<span class="tooltipRtext"><ul style="color:white;">
<li>Differential Signaling</li>
<li>Full-Duplex</li>
</ul></span></span></div>

<li>I2C</li>
<li>SPI</li>
<li>GPIO</li>
<li>USB</li>
<li>eUSCI</li>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('wifi)"><li style="color:gray;">Wireless</li></a>
<span class="tooltipRtext"><ul style="color:white;">
<li>Wifi (WLAN)</li>
<li>Bluetooth</li>
<li>Zigbee</li>
<li>RFID</li>
<li>GSM and GPS</li>
</ul></span></span></div>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('uart)"><li style="color:gray;">Mixed-Signals</li></a>
<span class="tooltipRtext"><ul style="color:white;">
<li>Analog</li>
<li>Digital</li>
<li>ADCs and DACs</li>
</ul></span></span></div>

</ul>

##### Internet of Things

* Communications
* Information
* Fourier Series and Transform
* Filters
* Networking    
    
### Digital Systems {.tabset .tabset-fade}

#### FPGAs and HDLs

<ul>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('verilog')"><li style="color:gray;">Verilog</li></a>
<span class="tooltipRtext">Developed using: Vivado <br/> on a Artix 7 and Kintex 7</span></span></div>
<ul>
<li>Behavioral</li> 
<li>Dataflow</li>
<li>Structural</li>
<li>System</li>
</ul>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('vhdl')"><li style="color:gray;">VHDL</li></a>
<span class="tooltipRtext">Developed using: Libero <br/> on a PolarFire</span></span></div>
</ul>
  
#### Simulation and Testing

<ul>

<li>Verilog Test Bench</li>
<li>Logisim</li>
<li>Waveform</li>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('IC')"><li style="color:gray;">Logic Integrated Circuits</li></a>
<span class="tooltipRtext"><ul style="color:white;">
<li>TTL (7400-Series)</li>
<li>CMOS</li>
</ul></span></span></div>
</ul>

### Computer Systems {.tabset .tabset-fade}

#### Computer Organization

* Memory Hierarchy 
* Computer Arithmetic
* Machine Optimization
* System Drivers
* Concurrency
* Parallelism

#### Processor Design

* Instruction Architecture
* Machine Level Instructions
* Control Unit Design
* Reduced Instruction Set 
* Triple Modular Redundancy

### Engineering Fundamentals {.tabset .tabset-fade}

#### Circuit Analysis

<ul>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('spice')"><li style="color:gray;">Spice Software</li></a>
<span class="tooltipRtext"><ul style="color:white;">
<li>LTSpice</li> 
<li>EasyEDA</li>
</ul></span></span></div>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('op')"><li style="color:gray;">Transistors, Diodes, and Op-Amps</li></a>
<span class="tooltipRtext"><ul style="color:white;">
<li>MOSFETS</li> 
<li>BJT</li>
</ul></span></span></div>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('BC')"><li>Basic Circuits</li></a></span>
<div id="BC" style="display:none;padding-left:20px;">
<p>Methods and Techniques:</p>
<ul>
<li>Nodal</li> 
<li>Mesh</li>
<li>Kirchhoff's Laws</li> 
<li>Thevenin's Theorem</li> 
<li>Norton's Theorem</li>
</ul></div></div>
<ul>
<li>Inductors</li> 
<li>Capacitors</li>
<li>Resistors</li>
</ul>

</ul>

#### Engineering Basics

<ul>

<li>Design and Communication</li>
<li>Ethics and Economics</li>
<li>Drawings and Draftings</li>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('EM')"><li style="color:gray;">Parameters Based Systems</li></a>
<span class="tooltipRtext"><ul style="color:white;">
<li>Length</li> 
<li>Time</li>
<li>Mass</li> 
<li>Force</li>
<li>Temperature</li>
<li>Energy and Power</li>
</ul></span></span></div></ul>

#### Science {.tabset .tabset-pills}

##### Physics

<ul>

<li>Mechanics</li>
<ul>
<li>Newtonian</li>
<li>Fluid</li>
<li>Kinematics</li>
<li>Statics</li>
<li>Dynamics</li>
</ul>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('MM')"><li style="color:gray;">Motion and Momentum</li></a>
<span class="tooltipRtext"><ul style="color:white;">
<li>Circular</li> 
<li>Harmonic</li>
<li>Rotational (Torque)</li> 
</ul></span></span></div>

<li>Waves and Sound</li>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('EM')"><li style="color:gray;">Electricity and Magnetism</li></a>
<span class="tooltipRtext"><ul style="color:white;">
<li>Electrical Systems, Fields and Forces</li> 
<li>Magnetic Systems, Fields and Forces</li>
<li>Electromagnetic Forces and Optics</li>
</ul></span></span></div>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('MP')"><li style="color:gray;">Modern Physics</li></a>
<span class="tooltipRtext"><ul style="color:white;">
<li>Quantum</li> 
<li>Atomic</li>
<li>Nuclear</li> 
<li>Relativity</li>
</ul></span></span></div>
  
</ul> 
  
##### Chemistry

* Strengths and Materials 
* Molecular and Ionic Compounds
* Intermoleular Forces
* Reactions, Kinetics and Equilibrium
* Acids and Bases

##### Thermodynamics

* Thermodynamic Systems and Entropy
* Heat Transfer and Thermal Equilibrium
* Endothermic and Exothermic Processes
* Energy of Phase Changes and Transfer
* Enthalpy of Formation and Reaction
* Hess’s Law and Ideal Gas Law
* Laws of Thermodynamics

## Data Science

### Tools

<ul>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('R')"><li>R</li></a>
<span class="tooltipRtext">Developed using: RStudio <br/> with Rmd files and R Scripts</span>
</span>
<div id="R" style="display:none;padding-left:20px;">

Packages include: 

<ul>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('tidy')"><li style="color:gray;">tidyverse</li></a>
<span class="tooltipRtext" style="color:white;"><ul style="color:white;">
<li>ggplot2</li> 
<li>dplyr</li>
<li>tidyr</li>
<li>readr</li>
<li>purr</li> 
<li>tibble</li>
<li>stringr</li>
<li>forcats</li></li>
</ul></span></span></div>

<li>knitr</li>
<li>stringi</li>
<li>reticulate</li>
<li>lubridate</li>
<li>dygraphs</li>
<li>sf (simple features)</li>
<li>leaflet</li>
<li>devtools</li>
<li>downloader</li>
<li>pagedown</li>
<li>pacman</li>
<li>installer</li>
<li>blogdown</li>
<li>mosaic</li>
<li>car</li>
<li>future</li>
<li>glue</li>
<li>shiny</li>
</ul></div></div>
  
<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('Py')"><li>Python</li></a>
<span class="tooltipRtext">Developed using: <br/> Google Colab <br/> with Jupyter Notebooks</span>
</span>
<div id="Py" style="display:none;padding-left:20px;">

Libraries include:

  + Pandas
  + Matplotlib
  + Numpy
  + Plotly
  + Math
  + Tensor Flow
  + SciPy
  + Random
</div></div>  
  
<li>Tableau</li>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('Databases')"><li>Databases</li></a></span>
<div id="Databases" style="display:none;padding-left:20px;">

<ul>
<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('spread')"><li style="color:gray;">Spreadsheets</li></a>
<span class="tooltipRtext"><ul style="color:white;">
<li>Excel</li> 
<li>Google Sheets</li>
<li>LibreOffice Calc</li>
<li>R Data Editor</li>
</ul></span></span></div>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('sql')"><li style="color:gray;">SQL</li></a>
<span class="tooltipRtext"><ul style="color:white;">
<li>Oracle</li> 
<li>MySQL</li>
</ul></span></span></div>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('nosql')"><li style="color:gray;">NoSQL</li></a>
<span class="tooltipRtext"><ul style="color:white;">
<li>MongoDB</li> 
</ul></span></span></div></div></ul>

### Statistics {.tabset .tabset-fade}

#### Tests

<ul>
<li>t-test</li>
<li>Wilcox</li>
<li>ANOVA</li>
<li>Kruskal-Wallis</li>
<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('Regres')"><li style="color:gray;">Regression</li></a>
<span class="tooltipRtext"><ul style="color:white;">
<li>Linear</li>
<li>Logistic</li>
</ul></span></span></div>
<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('Chi')"><li style="color:gray;">Chi-Squared</li></a>
<span class="tooltipRtext"><ul style="color:white;">
<li>Independence</li>
<li>Goodness of Fit</li>
</ul></span></span></div>
<li>Permutation and Randomization</li>
</ul>

#### Topics

<ul>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('Dis')"><li style="color:gray;">Distributions</li></a>
<span class="tooltipRtext"><ul style="color:white;">
<li>Normal (Z) Distribution</li>
<li>Chi Squared Distribution</li>
<li>t Distribution</li>
<li>F Distribution</li>
</ul></span></span></div>

<li>Z Scores</li>
<li>P Values</li>
<li>Experimental Design</li>
<li>Probability Theory</li>
<li>Confidence Intervals</li>
<li>Hypothesis Testing</li>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('dat')"><li>Data Management</li></a></span>
<div id="dat" style="display:none;padding-left:20px;">
+ Intuition
+ Insight 
+ Wrangling 
+ Visualization
+ Exploration
+ Consulting
+ Mining
</div></div>

</ul>

### Machine Learning

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('ML')"><div style="color:gray;">Algorithms include:</div></a>
<span class="tooltipRtext">Developed using Python</span></span></div>

* Classifiers
* Clustering
* Decision Trees
* K-Nearest Neighbors
* Neural Networks

## Information Technology

### Web Development

<ul>

<li>HTML</li>
<li>CSS</li>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('JS')"><li style="color:gray;">JavaScript</li></a>
<span class="tooltipRtext">W3 Schools Quiz: 21/25</span>
</span></div>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('CS')"><li style="color:gray;">C#</li></a>
<span class="tooltipRtext">W3 Schools Quiz: 23/25</span>
</span></div>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('php')"><li style="color:gray;">PHP</li></a>
<span class="tooltipRtext">W3 Schools Quiz: 21/25</span>
</span></div>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('Pyweb')"><li>Python Web App</li></a></span>
<div id="Pyweb" style="display:none;padding-left:20px;">
* Python libraries
  - Flask
  - Django
* Google SDK  
</div></div>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('Rweb')"><li>R-based webpages</li></a></span>
<div id="Rweb" style="display:none;padding-left:20px;">

* Basic knitr    
  Basic building blocks:
  - knitr (R package)
  - _site.yml
  - index.Rmd
* Blogdown    
  Basic building blocks:
  - blogdown (R package)
  - config.toml
  - index.Rmd
* Bookdown    
  Basic building blocks:
  - bookdown (R package)
  - _bookdown.yml
  - _output.yaml
  - index.Rmd
* Pagedown    
  Basic building blocks:
  - pagedown (R package and templates)
  - knitr (R package)
  - Rmarkdown
* Shiny App    
  Basic building blocks:
  - shiny (R package)
  - app.R or ui.R/server.R
    <ul>
    <div style="padding-left:0px;">
    <span class="tooltipr"><a href="javascript:showhide('shinyui')"><li>User Interface</li></a></span>
    <div id="shinyui" style="display:none;padding-left:20px;">
      ```
      ui <- fluidPage(
        titlePanel("title panel"),

        sidebarLayout(
          sidebarPanel("sidebar panel"),
          mainPanel("main panel")
        )
      )
      ```
    </div></div>
    <div style="padding-left:0px;">
    <span class="tooltipr"><a href="javascript:showhide('shinyserver')"><li>Shiny Server</li></a></span>
    <div id="shinyserver" style="display:none;padding-left:20px;">
      ```
      server <- function(input, output) {
      
      }
      ```
    </div></div></div></div> 
    
</ul>  

### Operating Systems

<ul>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('JS')"><li style="color:gray;">Linux</li></a>
<span class="tooltipRtext"><ul style="color:white;">
<li>Ubuntu</li>
<li>Fedora</li>
<li>Crouton</li>
<li>Debian</li>
<li>Mint</li>
<li>Kali</li>
</ul></span></span></div>

<li>Chrome OS</li>
<li>Android OS</li>

<li>Microsoft Windows</li>
<ul>
<li>Office 365</li>
<li>Active Directory</li>
</ul>

<li>Virtual Machines</li>
<ul>
<li>VirtualBox</li>
<li>VMware</li>
</ul>

<li>Command lines</li>
<ul>
<li>Bash</li>
<li>Batch</li>
<li>Powershell</li>
<li>Windows Task Scheduler</li>
</ul>

</ul>  

### Security  

* Malware and Antimalware
* Social Engineering
* Cryptography
* Data and Networks 
* Authentication and Access
* Application and Device
* Business Continuity
* Risk Mitigation
* Binary Analysis

### Cloud Computing

* Git
  + Github
  + Bash
* Google Cloud
  + Drive
  + Colab
* Docker
* Kubernetes
* Network Computing
  + Virtual Network Computing (VNC)
  + Secure Shell (SSH)
  + Remote Desktop Protocol (RDP)
  
### Project Management

<ul>

<li>Technical Teamwork</li>
<li>Risk Management</li>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('method')"><li style="color:gray;">Methodologies</li></a>
<span class="tooltipRtext"><ul style="color:white;">
<li>Agile</li>
<li>Scrum</li>
<li>Waterfall</li>
</ul></span></span></div>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('kanban')"><li style="color:gray;">Kanban Board</li></a>
<span class="tooltipRtext"><ul style="color:white;">
<li>Trello</li>
<li>Jira</li>
</ul></span></span></div></ul> 

### General CIT

* Networking
* DevOps
* System Administration 
* Databases
  + Development 
  + Design
  + Programming
  + Administration

## Mathematics

<ul>

<li>Differential Calculus</li>
<li>Linear Algebra</li>
<li>College Algebra</li>
<li>Trigonometry</li>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('ba')"><li>Boolean Algebra</li></a></span>
<div id="ba" style="display:none;padding-left:20px;">

Topics include:

* Numbers Systems
* Signed Numbers
  + Signed Magnitude
  + 1's Complement
  + 2's Complement
* Theorems and Identities
  + Simplification and Minimization
  + Consensus
  + DeMorgan's Rules
  + Sum of Products and Product of Sums
  + Canonical Forms
  + Karnaugh Maps

</div></div>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('dm')"><li>Discrete Math</li></a></span>
<div id="dm" style="display:none;padding-left:20px;">

Topics include:

* Sets and Logic
* Functions and Relations
* Combinatorics and Probability
* Number Theory and Practice
* Trees and Graphs
* Languages and Grammars

</div></div>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('math')"><li style="color:gray;">Basic Math and Arithmetic</li></a>
<span class="tooltipRtext">W3 Schools Quiz: 25/25</span>
</span></div></ul>  

### Functional Programming
    
* MATLAB
* Mathematica
* Elisp
* Erlang

## General Programming

### Languages

<ul>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('C++')"><li style="color:gray;">C/C++</li></a>
<span class="tooltipRtext">W3 Schools Quiz: 25/25<br/><br/>Developed Using:
<ul style="color:white;">
<li>Visual Studio</li>
</ul></span></span></div>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('Java')"><li style="color:gray;">Java</li></a>
<span class="tooltipRtext">W3 Schools Quiz: 22/25<br/><br/>Developed Using:
<ul style="color:white;">
<li>IntelliJ</li>
<li>Android Studio</li>
</ul></span></span></div>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('Python')"><li style="color:gray;">Python</li></a>
<span class="tooltipRtext">W3 Schools Quiz: 25/25<br/><br/>Developed Using:
<ul style="color:white;">
<li>Pycharm</li>
<li>Thony</li>
<li>Jupyter Notebook</li>
</ul></span></span></div>
</ul>  

### Design Patterns

* Multithreading
* UML Diagrams
* Model–view–controller
* Test Driven Development
* Observer
* Factory
* Singleton
* Adapter
* Template
* Composite

### Data Structures

* Arrays
* Stacks
* Heaps
* Queues
* Graphs
* Trees
* Linked Lists
* Hash Tables

## Industry Knowledge

### Interpersonal Skills

* Technical Communication
* Human Relations
* Problem Solving
* Teaching
* Leadership
* Organization
* Finance

### Research

* Scientific 
* Computational
* Security
* Market 
* Data

`r pagebreak()`

<footer><div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('copyright')"><p style="color:blue;">`r copyright()`</p></a></span>
<div id="copyright" style="display:none;padding-left:20px;">`r licence()`</div></div></footer>