---
title: "Work Experience"
---

```{r load_libraries, include=FALSE}
knitr::opts_chunk$set(results = 'asis', echo = FALSE, message = FALSE, warning = FALSE)
pacman::p_load(tidyverse, glue)

source("./site_libs/script.R")
datapath <- "./site_libs/data/"
```

<script src="./site_libs/script.js"></script>

```{r}
entries <- read_csv(glue("{datapath}entries.csv"))
print_work(entries)
```

## Brigham Young University - Idaho 

### Teaching Assistant {.tabset .tabset-fade}

#### C Programming 

July 2020 – December 2020 --- Remote

* Help students learn C and C++ programming language 
* Assist the professor in creating new material

#### Intro Engineering 

January 2020 – December 2020 --- Rexburg, ID and Remote

* Mentor new students in Engineering and Computer Science
* Help students with basic circuit analysis
* Lead students in learning arduino skills

#### Digital Systems 

September 2018 – December 2020 --- Rexburg, ID

*	Lead students to increase their knowledge of Digital Systems
*	Guide students to improvement by giving feedback
*	Help students with programming Verilog 

#### Discrete Math

April 2019 - July 2019 --- Rexburg, ID

* Solved example problems to assist students with Discrete Math
* Assisted students in learning Elisp and Erlang

### Computer Science Tutor 

April 2018 - August 2018 --- Rexburg, ID

<ul>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('tutor')"><li>Tutored many classes</li></a></span>
<div id="tutor" style="display:none;padding-left:20px;">
  Including:
  
  + Object-Oriented Programming with Data Structures using Python
  + Fundamentals of Digital Systems w/ Lab
  + Introduction to Engineering
  + Introduction to Electrical and Computer Engineering 
  
</div></div>

<li>Taught students topics from these classes</li>
<li>Lead group and individual appointments and discussions</li>

</ul>

<hr />

<iframe src="./site_libs/footer.html" width="100%" height="100%" style="border:none;"></iframe>