---
title: "Work Experience"
editor_options: 
  chunk_output_type: console
---

<!--
This program is free software: you can redistribute it and/or modify
it under the terms of the GNU General Public License as published by
the Free Software Foundation, either version 3 of the License, or
(at your option) any later version.

This program is distributed in the hope that it will be useful,
but WITHOUT ANY WARRANTY; without even the implied warranty of
MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
GNU General Public License for more details.

You should have received a copy of the GNU General Public License
along with this program.  If not, see <https://www.gnu.org/licenses/>.
-->

```{r load_libraries, include=FALSE}
source("./site_libs/script.R")
datapath <- "./site_libs/data/"
load_libraries()

entries <- read_csv(glue("{datapath}entries.csv"))
```

```{r eval=FALSE}
render_all()
```

```{r}
nav()
print_work(entries)
```

## Brigham Young University - Idaho 

#### Part-Time

### Teaching Assistant {.tabset .tabset-fade}

```{r}
print_TA(entries)
```

### Computer Science Tutor 

April 2018 - August 2018 --- Rexburg, ID

<ul>

<div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('tutor')"><li>Tutored many classes</li></a></span>
<div id="tutor" style="display:none;padding-left:20px;">
  Including:
  
  + Object-Oriented Programming with Data Structures using Python
  + Fundamentals of Digital Systems w/ Lab
  + Introduction to Engineering
  + Introduction to Electrical and Computer Engineering 
  
</div></div>

<li>Taught students topics from these classes</li>
<li>Lead group and individual appointments and discussions</li>

</ul>

`r pagebreak()`

<footer><div style="padding-left:0px;">
<span class="tooltipr"><a href="javascript:showhide('copyright')"><p style="color:blue;">`r copyright()`</p></a></span>
<div id="copyright" style="display:none;padding-left:20px;">`r licence(work)`</div></div></footer>