---
title: "Task 11"
subtitle: "Strings and grep"
author: "Kyle Tolliver"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
library(tidyverse)
```

```{r load_data}
# Use this R-Chunk to import all your datasets!
let <- readr::read_lines("https://byuistats.github.io/M335/data/randomletters.txt") 
letnum <- readr::read_lines("https://byuistats.github.io/M335/data/randomletters_wnumbers.txt")
```

## Background

Using global regular expression print (grep) and regular expressions (regex) to find character string patterns is a valuable tool in data analysis and is available with all operating systems and many different programming languages. It is a powerful tool once it is understood. The recently developed library(stringr) package makes these tools much easier to use. The three tasks below can be completed in many different ways. As a challenge, my code to complete this entire task less than 10 lines.

## Reading

* Chapter 14: R for Data Science - Strings
* RVerbalExpressions package

## Tasks

[X] Use the readr::read_lines() function to read in each string - randomletters.txt and randomletters_wnumbers.txt

[X] With the randomletters.txt file, pull out every 1700 letter (e.g. 1, 1700, 3400, …) and find the quote that is hidden - the quote ends with a period

[X] With the randomletters_wnumbers.txt file, find all the numbers hidden and convert those numbers to letters using the letters order in the alphabet to decipher the message

[X] With the randomletters.txt file, remove all the spaces and periods from the string then find the longest sequence of vowels.

[X] Save your .R script to your repository and be ready to share your code solution at the beginning of class

## Data Wrangling


```{r letter1700}
letter1700 <- let %>% 
  str_split("") %>% 
  unlist() %>% 
  .[c(1, seq(0, str_count(let), 1700))] %>% 
  str_flatten() %>% 
  str_remove_all('\\..*$')

letter1700
```

```{r numlet}
numlet <- letnum %>% 
  str_extract_all('[:digit:]+') %>% 
  unlist() %>% 
  as.integer() %>% 
  letters[.] %>% 
  paste(collapse = '')
  
numlet
```

```{r letspace}
spacelet <- let %>% 
  str_remove_all('\\.') %>% 
  str_remove_all('[:space:]') %>% 
  str_locate('[aeiou]')
  
spacelet
```

## In Class    
### Partner Practice

```{r partner}
aeletters <- str_extract_all(letters, c("a", "e")) 
str_length(aeletters)

jim <- str_count(letters, "jim")
jim

multiples <- str_extract_all(letters, "(.)\\1\\1")
multiples

aaa <- str_locate_all(letters, "aaa")
aaa

split <- str_split(letters, "")
split
```