---
title: "BYUI"
subtitle: "Grad Plan"
output: 
  html_document: 
    keep_md: true
    toc: true
    toc_float: true
---

```{r library, include=FALSE}
library(knitr)
library(tidyverse)

post_bac <- read_csv("./Post.csv")
tech <- read_csv("./Tech.csv")
semester <- read_csv("./Semester.csv")
```

[GPA Calculator](https://docs.google.com/spreadsheets/d/17MqEXr2rU52hgKAC0EaDHCsJDcDCpSD8Tjf-FzIeY3Y/edit#gid=232978671)

## Software Engineering 

#### [(BS)](https://www.byui.edu/catalog#/programs/4kNfm-2oZ?bc=true&bcCurrent=Software%20Engineering&bcGroup=Department%20of%20Computer%20Science%20and%20Electrical%20Engineering&bcItemType=programs)

### Computing Fundamentals

Take the following:

* [X] CSE 100 - Introduction to Computing (1)
* [X] CSE 170 - Introduction to Technical Teamwork (2)
* [X] CIT 171 - Introduction to Cybersecurity (2)
* [X] ECEN 106 - Computer Systems (2)
* [X] WDD 130 - Web Fundamentals (2)
* [X] CIT 111 - Introduction to Databases (3)
* [X] CSE 150 - Data Intuition and Insight (2)

### Computer Programming

Take the following:

* [X] CSE 110 - Programming Building Blocks (2)
* [X] CSE 111 - Programming with Functions (2)
* [X] CSE 121B - JavaScript Language (1)
* [X] CSE 210 - Programming with Classes (2)
* [X] CSE 212 - Programming with Data Structures (2)
* [X] CSE 310 - Applied Programming (4)

### Capstone

Take the following:

* [X] CSE 398 - Internship (1 - 4)
* [X] CSE 499 - Senior Project (3)

### Embedded Systems Certificate

Take the following: 

* [X] CSE 121C - C Language (1)
* [X] ECEN 240 - Fundamentals of Digital Systems (3)
* [X] ECEN 260 - Microprocessor Based-System Design (3)
* [X] ECEN 324 - Computer Architecture (3)
* [X] ECEN 361 - Embedded Systems (3)

## Data Science 

#### [(AAS)](https://www.byui.edu/catalog#/programs/Ey-19J50W?bc=true&bcCurrent=Data%20Science&bcGroup=Department%20of%20Mathematics&bcItemType=programs)

### Programming Fundamentals    

Take the following: 

* [X] CIT 111 - Introduction to Databases (3)
* [X] CSE 110 - Programming Building Blocks (2)
* [X] CSE 111 - Programming with Functions (2)
* [X] CSE 210 - Programming with Classes (2)
* [X] CSE 310 - Applied Programming (4)

Take 1 of following:

* [ ] CSE 250 - Data Science Programming (2)
* [ ] CSE 450 - Machine Learning and Data Mining (3)

### Mathematical Foundations

* [X] CSE 150 - Data Intuition and Insight (2)
* [X] MATH 112 - Calculus I (4)
* [ ] MATH 325 - Intermediate Statistics (3) 
* [X] MATH 335 - Data Wrangling, Exploration, and Visualization (3)

### Design & Communication   

Take the following: 

* [X] BUS 301 - Advanced Writing in Professional Contexts (3)

Take 1 of following (Design Thinking):

* [ ] ART 231 - Inquiry and Innovation (3)
* [ ] ART 432 - Customer Experience (3)
* [ ] ART 434 - Agile Product Management (3)

### Technical Depth    
  
Take at least 7 credits from: 

* [X] CIT 225 - Database Design & Development (3)
* [X] CSE 280 - Discrete Mathematics I (2)
* [X] MATH 341 - Linear Algebra (3)
* [X] WDD 130 - Web Fundamentals (2)

## Fall 2020

```{r table, echo=FALSE}
kable(post_bac)
```

```{r distinct, include=FALSE}
bac <- post_bac %>% unique() %>% 
  group_by(Code, Name, Department, Crds) %>%
  summarise(min_crds = min(Crds)) %>% 
  summarise(sum_crds = sum(min_crds))

str <- str_split(bac$sum_crds, pattern = "")

num_str <- as.numeric(str)

sum <- sum(num_str)

sent <- "total credits ="
```

```{r display, echo=FALSE}
print(paste(sent, sum))
```

### Technical Elective 

```{r tech, echo=FALSE}
kable(tech)
```