---
title: "Boise-MS"
output: 
  html_document:
    keep_md: true
    toc: true
    toc_float: true
---

```{r library, include=FALSE}
library(tidyverse)
library(knitr)

boise <- read_csv("./boise1.csv")
ds <- read_csv("./boise2.csv")
```

## Degree Requirements

The degree requirements described above allow the student a fair amount of flexibility in designing a program to fit their needs. The course work is to be chosen by the student, in consultation with his/her advisor and the Computer Science Graduate Committee. The Master of Science in Computer Science requires a minimum of 30 credit hours, as specified in the table below. The student can take up to three credits of independent study. The student can also take up to three credits of Practicum (industrial internship). In addition, the student’s advisor and the Computer Science Graduate Coordinator must approve the student’s proposed degree plan to ensure that it meets these criteria and forms a coherent program of study. All requirements for the degree must be completed within five years of initial enrollment in the program, unless the Computer Science Graduate Committee grants an explicit extension of time. In no event will more than seven years be allowed for completion of the degree.

```{r kable, echo=FALSE}
kable(boise)
```

### Data Science Emphasis

* CS 533: Introduction to Data Science	
  + CS 321: Data Structures   
  (1 of the following)
  + MATH 360: Engineering Statistics
  + MATH 361: Probability And Statistics I
  + MATH 471: Data Analysis
* CS 534: Machine Learning
  + CS 533: Introduction To Data Science
* MATH 562: Probability And Statistics	
  + MATH 275: Multivariable And Vector Calculus
  + MATH 301: Introduction To Linear Algebra 
  + MATH 361: Probability And Statistics I
* MATH 572: Computational Statistics	
  + MATH 361: Probability And Statistics I

```{r ds, echo=FALSE}
kable(ds)
```
  
## Possible Electives

### CS

* CS 507: Computing Foundations for Computational Science
* CS 535: Large-Scale Data Analysis
  + CS 533: Introduction to Data Science
* CS 536: Natural Language Processing  
* CS 550: Programming Language Translation
  + CS 253: Introduction to Systems Programming
  + CS 321: Data Structures
  + CS 354: Programming Languages 
* CS 557: Artificial Intelligence  
  + CS 321: Data Structures
  + CS 354: Programming Languages 
* CS 561: Theory of Computation   
* CS 564: Visualization Techniques
  + CS 321: Data Structures
* CS 565: Numerical Methods I (Math 565) 
  + MATH 365: Introduction to Computational Mathematics
* CS 633: Deep Learning  
  + CS 533: Introduction to Data Science
  + MATH 301: Introduction to Linear Algebra

* COMPUT 571: Parallel Scientific Computing

### MATH

* MATH 501: Foundations of Mathematics
  + MATH 143: College Algebra
* MATH 556: Linear Programming  
  + MATH 301: Introduction to Linear Algebra
* MATH 564: Mathematical Modeling  
  + MATH 361: Probability and Statistics I
* MATH 571: Data Analysis 
  + MATH 361: Probability and Statistics I

### Business

* MBA 507: Statistical Thinking and Business Analytics
* MBA 509: Data Management and Analytics

## Other Emphasis

### Computational Science and Engineering

* COMPUT 571: Parallel Scientific Computing	
* CS 507: Computing Foundations for Computational Science	
* CS 565: Numerical Methods I	(MATH 565)
* CS 566: Numerical Methods II (MATH 566)

### Computer Science

* CS 521: Design and Analysis of Algorithms
* CS 561: Theory of Computation
* CS 552: Operating Systems
* CS 573: Advanced Software Engineering

### Cybersecurity

* CS 546: Computer Security	
* CS 567: Applied Cryptography 
* MATH 508: Adv Asymmetric Cryptography & Cryptanalysis 
* MATH 509: Symmetric Key Cryptology & Cryptanalysis	
* CS 575: Software Security 
* CS 622: Advanced Network Security