---
title: "NYU-MS"
output: 
  html_document:
    keep_md: true
    toc: true
    toc_float: true
---

```{r library, include=FALSE}
library(tidyverse)
library(knitr)

nyu <- read_csv("./nyu.csv")
```

## Program Requirements

The curriculum is 36 credits, and offers two ways to structure the graduate program that gives students the opportunity to pursue a specialization through tracks.

Both full-time and part-time students must complete all 36 credits within 5 years of enrolling at NYU as an MS in Data Science candidate.

See [Master’s in Data Science](https://cds.nyu.edu/masters-program/)

### Required

* DS-GA 1001 [Introduction to Data Science](https://github.com/briandalessandro/DataScienceCourse)
* DS-GA 1002 [Probability and Statistics for Data Science](http://www.cims.nyu.edu/~cfgranda/pages/DSGA1002_fall17/index.html)
* DS-GA 1003 [Machine Learning](https://davidrosenberg.github.io/ml2019/#home)
* DS-GA 1004 Big Data
* DS-GA 1006 Capstone Project and Presentation
* One Data Science Elective (choose 1 from the list below).
  + DS-GA 1005 [Inference and Representation](https://inf16nyu.github.io/home/)
  + DS-GA 1008 Deep Learning
  + DS-GA 1011 [Natural Language Processing with Representation Learning](https://docs.google.com/document/d/1SIPSt4aeB3Lys9ztCp47Y4v68R6Awt8NBTlCObp2njg/edit?usp=sharing)
  + DS-GA 1012 Natural Language Understanding and Computational Semantics
  + DS-GA 1013 [Mathematical Tools for Data Science](https://cims.nyu.edu/~cfgranda/pages/MTDS_spring19/index.html)
  + DS-GA 1014 Optimization and Computational Linear Algebra
  
### Electives  

* DS-GA 1007 Programming for Data Science
* DS-GA 1009 Practical Training for Data Science
* DS-GA 1010 Independent Study
* DS-GA 3001 Special Topics in Data Science: Probabilistic Time Series Analysis
* DS-GA 3001 Special Topics in Data Science: Insurance & Applied Insurtech
* DS-GA 3001 Special Topics in Data Science: Intro to Computer Vision
* DS-GA 3001 Special Topics in Data Science: Data Engineering for Machine Learning
* DS-GA 1009 Practical Training for Data Science
* DS-GA 1010 Independent Study
* DS-GA 1015 Text as Data
* DS-GA 3001 Special Topics in Data Science: Advanced Python for Data Science
* DS-GA 3001 Special Topics in Data Science: Computational Cognitive Modeling
* DS-GA 3001 Special Topics in Data Science: Responsible Data Science
* CSCI-GA 1170 Fundamental Algorithms
* CSCI-GA 2433 Database Systems
* MATH-GA 2751 Risk & Portfolio Management with Econometrics
* CSCI-GA 2566 Foundations of Machine Learning
* BIOL-GA 1127/CSCI-GA 2520 Bioinformatics & Genomes
* CSCI-GA 3033 Special Topics Computer Science: Statistical Natural Language Processing
* CS-GY 6003 Foundations of Computer Science
* STAT-GB 2302 Forecast Time Series Data
* STAT-GB 3383 Frequency Domain Time Series
* STAT-GB 2301 Regression & Multivariate Data Analysis

### 4 Semester Plan

```{r kable, echo=FALSE}
kable(nyu)
```

## Data Science Tracks

In the Data Science track, students take six required courses and six elective courses from a diverse list of courses.

### Data Science Big Data Track

The Data Science Big Data track focuses on methods and techniques required to acquire, manage, analyze and visualize large volumes of data. Student will acquire deep understanding of algorithms and their complexity and gain hands-on experience on how to build end-to-end solutions to computational problems.

Ordinarily, students pursuing this track take 3 of the following courses –

* DS-GA 1012: Natural Language Understanding and Computational Semantics
* CS-GY 6313: Information Visualization
* CS-GY 6323 Large-Scale Visual Analytics
* One of the following:
  + CS-GY 6083 Principles of Database Systems (Engineering School) 
  + CSCI-GA 2433 Database Systems (Courant Computer Science)
  + CS-GY 6093: Advanced Database Systems (Engineering School) 
  + CSCI-GA 2434 Advanced Database Systems (Courant Computer Science)

### Data Science Mathematics and Data Track

The Data Science Mathematics and Data track provides the mathematical background to understand and analyze modern data-analysis methods in areas such as deep learning, compressed sensing, high-dimensional statistics and graph signal processing. In addition, the track will provide exposure to fundamental research problems inspired by newly-developed data-science techniques.

Ordinarily, students pursuing this track take 2 of the following courses –

* DS-GA 1013: Mathematical Tools for Data Science
* DS-GA 1005: Inference and Representation
* DS-GA 3001.010/.011 Special Topics in Data Science –  Mathematics of Data Science: Graphs and Networks
* CSCI-GA 2945/MATH-GA 2012 Convex and Nonsmooth Optimization
* CSCI-GA 3033/DS-GA 3001 Special Topics: Mathematics of Deep Learning

### Data Science Natural Language Processing Track

The Data Science Natural Language Processing Track will give students the skills to build machine learning models that can understand, manipulate, or produce data expressed in natural language text.

Ordinarily, students pursuing this track take the following 2 courses in order:

* DS-GA 1011 Natural Language Processing with Representation Learning
* DS-GA 1012 Natural Language Understanding and Computational Semantics
* CSCI-GA 3033 Statistical Natural Language Processing

Recommended courses:

* DS-GA 1005 Inference and Representation
* DS-GA 1008 Deep Learning
* DS-GA 3001 Text as Data
* CSCI-GA 2590 Natural Language Processing

Advanced linguistics courses with consent of instructor. Contact Sam Bowman (bowman@nyu.edu) for advice.

### Data Science Physics Track

The Data Science Physics Track provides the same solid foundation in data science and further develops modeling and inference skills in the context of compelling, data-intensive physics research topics. This track is ideal for applicants who have some physics background, are interested in transitioning into a career in data science, and wish to leverage those skills for a competitive advantage.

Ordinarily, students pursuing this track take the following courses –

* DS-GA 1005 Inference and Representation
* Physics Research: Select 2 of the following –
  + PHYS-GA 2091 Experimental Physics Research
  + PHYS-GA 2093 Theoretical Physics Research
  + PHYS-GA 2095 Research Reading
* Physics Electives: Select 2 of the following –
  + PHYS-GA 2000 Computational Physics
  + PHYS-GA 2002 Statistical Physics
  + PHYS-GA 2022 Biophysics
  + PHYS-GA 2059 Special Topics
  + PHYS-GA 2061 Special Topics
  + PHYS-GA 2053 Special Topics in Astrophysics
  + PHYS-GA 2054 Special Topics in Astrophysics
  + PHYS-GA 2017 Phase Transitions and Critical Phenomena

### Data Science Biology Track 

Large datasets are revolutionizing our understanding of basic biology as well as of human health and disease. The Data Science Biology track is for students who want to further develop their computational skills and apply them to the biomedical sciences.

The capstone project for this track will be biology-based and completed with a biology or biotech mentor. Ordinarily, students pursuing this track take the following courses – 5 Biology electives

* Semester 1: 1 of the following 
  + BIOL-GA 1001 Biocore I: Molecular Systems
  + BIOL-GA 1128 Systems Biology
* Semester 2: 1 of the following  
  + BIOL-GA 1002 Biocore II: Cellular Systems 
  + BIOL-GA 1130 Applied Genomics
* Semester 3: 1 of the following  
  + BIOL-GA 1128 Systems Biology 
  + BIOL-GA 1040 Genomic Innovation 
* Semester 4: 2 from each group 
  + Group 1
    - BIOL-GA 3304 Research 
    - BIOL-GA 2005 Current Topics in Biology
  + Group 2 
    - BIOL-GA 1127 Bioinformatics and Genomes 
    - BIOL-GA 1131 Biophysical Modeling 
    - BIOL-GA 3304 Research in Biology

### Data Science – Biomedical Informatics Track 

The Data Science – Biomedical Informatics track is for students who are interested in the rapidly growing field of biomedical informatics, which has influenced many recent healthcare developments, including new opportunities for personalized medicine. These innovations, along with a recent growth in high-throughput genomics technologies, have created a high demand for skilled biomedical informatics professionals.

The capstone project for this track will be biomedicine-based and completed with a biomedicine mentor. In addition to the 6 required courses, ordinarily, students pursuing this track take the following courses –

* Biomedicine Research: Select 2 of the following –
  + BMIN-GA 0003 Introduction to Biomedicine
  + BMIN-GA 1003 Introduction to Health Informatics
  + BMIN-GA 3001 Topics in Bioinformatics
* Biomedicine Electives: Select 2 of the following –
  + BMIN-GA 3009 Advanced Integrative Omics
  + BMIN-GA 3002 Clinical Decision Support Systems
  + BMIN-GA 3007 Deep Learning for Biomedical Data
  + BMIN-GA 3008 Evaluation Methods in Health IT
  + BMIN-GA 3010 Microbiome Informatics
  + BMIN-GA 3004 Next Generation Sequencing
  + BMIN-GA 3003 Proteomics Informatics
