---
title: "Task 7"
subtitle: "Data to Answer Questions"
author: "Kyle Tolliver"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
  editor_options: 
    chunk_output_type: console
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
library(tidyverse)
library(nycflights13)
here <- here::here()
setwd(here)
```

```{r load_data}
# Use this R-Chunk to import all your datasets!

```

## Background

Finding good data takes time, and can take longer than the time to tidy your data. This task could easily take 3-6 hours to find the data you need for your semester project. After you find good data sources make sure to complete the remaining tasks.

## Reading

* What do people do with new data
* Finding data to answer your question
* Find a post from the functional art
* Chapter 20: R for Data Science - Vectors
* Chapter 18: R for Data Science - Pipes

## Tasks

[X] Take notes on your reading of the specified ‘R for Data Science’ chapter in the README.md or in a ‘.R’ script in the class task folder

[X] Review the “What do people do with new data" link above and write one quote that resonated with you in your .Rmd file.

[ ] Build an interactive document that has links to sources with a description of the quality of each

* [ ] Find 3-5 potential data sources (that are free) and document some information about the source
* [ ] Build an R script that reads in, formats, and visualizes the data using the principles of exploratory analysis
* [ ] Write a short summary of the read in process and some coding secrets you learned
* [ ] Include 2-3 quick visualizations that you used to check the quality of your data
* [ ] Summarize the limitations of your final compiled data in addressing your original question

[X] After formatting your data identify any follow on or alternate questions that you could use for your project

## Data 

### Sources

#### Embedded Systems

1. [What radiation levels switch the states of the FPGA?](https://www.sciencedirect.com/science/article/pii/S1738573317302723)

2. [Most used Embedded System in industry?](https://www.totalphase.com/blog/2017/06/embedded-systems-applications-across-industries/)

3. [Most used language in Embedded Systems (other than Embedded C)?](https://www.ubuntupit.com/top-15-best-embedded-systems-programming-languages/)   

4. Most common used social engineering technique?

#### MATH/CS 335

1. What is the average grade of the students that attend RLab?
2. Are student that go to RLab higher then then those that don't?
3. Grade earned compared to Major?
4. Does those that have taken MATH/CS 335 do better in CS 450?
5. Does those that have taken MATH 325 do better in MATH/CS 335?

#### Job Comparsions

1. [What is the salary of data Sciencists?](https://neuvoo.com/salary/?job=data+scientist)    
1a. Best state to work in?

2. [What is the income of an Embedded Systems Engineer?](https://neuvoo.com/salary/?job=Embedded%20Systems%20Engineer)   
2a. Best state to work in?

3. [What is the salary of a Security Specialist?](https://neuvoo.com/salary/?job=Security+Admin)    
3a. Best state to work in?

### Analysis and Visualizations

See neuvoo.com

### Process

* Read in data
* Format it
* Analysis Data
* Visualize

### Limitations

* Not enough data
* Data not well organized
* Time to Analysis 
* Resources 

### Follow on questions

I came across that the questions I came up with first don't have enough data. 
I also had questions about 335 it self so Hathaway said there isn't data for that. 

How do I get the data needed to analysis (answer these questions)? 

## Reading Notes

### Ch 20 - Vectors

* Atomic vectors, of which there are six types: logical, integer, double, character, complex, and raw. 
* Integer and double vectors are collectively known as numeric vectors.
* Lists, which are sometimes called recursive vectors because lists can contain other lists.

### Ch 18 - Pipes

%<>% - Assignment with pipe

### What do people do with new data 

"Interview the source, if possible, to know all of the problems with the data, use limitations, caveats, etc." — Evan Thomas Paul

## Class Notes   
### STEM Fair