---
title: "Cover Letter"
author: "Kyle Tolliver"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  word_document:
    toc: yes

  html_document:
    code_folding: hide
    fig_align: center
    fig_height: 6
    fig_width: 12
    keep_md: yes
    toc: yes
    toc_float: yes
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
library(tidyverse)
```

## Background

Please write your cover letter to me about the class that uses the syllabus to justify your grade.

* Stating the key concepts and techniques
* Your learning during projects
* Your goals to continue learning in this area
* Include a grade request that represents your knowledge and task completion

## Conclusions

I feel like I have earned an A. I have completed all work. I submitted 18+ tasks on time as was required. I submitted 8+ case studies on time. I lead 3 case study discussions. And worked diligently to complete my semester project. You can verify on my course tracker page to see that I have completed all assignments, I also added a date section which allows you to see what date I finished each assignment. 

I learned a lot of different concepts this semester. I picked up R really fast. I learned many different packages that are used by Data Scientists, which include lubridate, tidyverse, sf, devtools, and more. I learned concepts about spatial mapping, interactive graphing, data wrangling, grep and many more. I learned many great things using Tidyverse package, which include ggplot2, dpylr, stringr and other sub packages. These are all fasinating to me. 

Learning for me is a never ending process. I plan to take Machine Learning and Data Mining (CSE 450) next semester. I then plan to go to grad school for System Reliablity, where I will take a few more data science and machine learning classes. I plan on dissertation having a great deal of data collection and analysis which will be done in R. As embark on an exciting career, I plan to stay up to date on R and it's packages. I also plan to use R in my life to help with stock investment, finance, morgage and more. What I have learned in this class will help me in the future no matter what I do as a career. 