---
title: "BYUI Data Science"
output: 
  html_document: 
    keep_md: true
    toc: true
    toc_float: true
---

```{r library, include=FALSE}
library(knitr)
library(tidyverse)

post_bac <- read.csv("./Post.csv")
```

## Fall 2020

```{r table, echo=FALSE}
kable(post_bac)
```

```{r distinct, include=FALSE}
bac <- post_bac %>% unique() %>% 
  group_by(Code, Name, Department, Crds) %>%
  summarise(min_crds = min(Crds)) %>% 
  summarise(sum_crds = sum(min_crds))

str <- str_split(bac$sum_crds, pattern = "")

num_str <- as.numeric(str)

sum <- sum(num_str)

sent <- "total credits ="
```

```{r display, echo=FALSE}
print(paste(sent, sum))
```

## Associates (AAS)

### Programming & Mathematical Fundamentals    

Take the following: 

* [X] CIT 111 - Introduction to Databases (3)
* [X] CSE 110 - Programming Building Blocks (2)
* [X] CSE 111 - Programming with Functions (2)
* [X] CSE 150 - Data Intuition and Insight (2)
* [X] CSE 210 - Programming with Classes (2)
* [ ] CSE 250 - Data Science Programming (2) 
* [X] MATH 112 - Calculus I (4)
* [ ] MATH 325 - Intermediate Statistics (3) 
* [X] MATH 335 - Data Wrangling, Exploration, and Visualization (3)

### Design & Comm    

Take the following:  

* [ ] ART 231 - Design Thinking: Inquiry and Innovation (3)
* [X] BUS 301 - Advanced Writing in Professional Contexts (3)

### Technical Depth    
  
Take 7 credit(s) from: 

* [X] CIT 225 - Database Design & Development (3)
* [X] CSE 280 - Discrete Mathematics I (2)
* [X] CSE 310 - Applied Programming (4)
* [ ] CSE 450 - Machine Learning and Data Mining (3) 
* [X] MATH 341 - Linear Algebra (3)
* [X] WDD 130 - Web Fundamentals (2)

## BYUI Programs 

* [Data Science](https://www.byui.edu/mathematics/student-resources/data-science)
  + [BS](https://www.byui.edu/catalog#/programs/41PwqJ9RZ?bc=true&bcCurrent=Data%20Science&bcGroup=Department%20of%20Mathematics&bcItemType=programs) 
  + [AAS](https://www.byui.edu/catalog/#/programs/Ey-19J50W?bc=true&bcCurrent=Data%20Science&bcGroup=Department%20of%20Mathematics&bcItemType=programs)
  + [Minor](https://www.byui.edu/catalog/#/programs/NyV_tJqAW?bc=true&bcCurrent=Data%20Science&bcGroup=Department%20of%20Mathematics&bcItemType=programs)
  + [Certificate](https://www.byui.edu/catalog/#/programs/N1ltkrR3Z?bc=true&bcCurrent=Data%20Science&bcGroup=Department%20of%20Mathematics&bcItemType=programs)
* [Computer Science](https://www.byui.edu/catalog#/programs/NyW7f7-nsZ?bc=true&bcCurrent=Computer%20Science&bcGroup=Department%20of%20Computer%20Science%20and%20Electrical%20Engineering&bcItemType=programs) - [Machine Learning Fundamentals Certificate](https://www.byui.edu/catalog#/programs/SkBbD40Y4/none?bc=true&bcCurrent=Machine%20Learning%20Fundamentals&bcGroup=Department%20of%20Computer%20Science%20and%20Electrical%20Engineering&bcItemType=programs)
* [Business Analytics](https://www.byui.edu/catalog#/programs/EkbQmWnob/none?bc=true&bcCurrent=Business%20Analytics&bcGroup=Department%20of%20Finance%20&bcItemType=programs)
* [Mathematical Sciences](https://www.byui.edu/catalog#/programs/By1hDTDCx/none?bc=true&bcCurrent=Mathematical%20Sciences&bcGroup=Department%20of%20Mathematics&bcItemType=programs)
  + [Applied Statistics](https://www.byui.edu/catalog#/programs/By1hDTDCx/4y5W50eRZ?bc=true&bcCurrent=Applied%20Mathematics&bcGroup=Department%20of%20Mathematics&bcItemType=programs)
    - [Statistics Concentration](https://www.byui.edu/catalog/#/programs/EJgKm7-3oW/NJ5dQ-hjZ?bc=true&bcCurrent=Software%20Management&bcGroup=Department%20of%20Interdisciplinary%20Studies&bcItemType=programs)
  + [Applied Mathematics](https://www.byui.edu/catalog#/programs/By1hDTDCx/4y8HAAeCZ?bc=true&bcCurrent=Applied%20Mathematics&bcGroup=Department%20of%20Mathematics&bcItemType=programs)
* [Biostatistics](https://www.byui.edu/catalog/#/programs/Vyl0fmZ2o-?bc=true&bcCurrent=Biostatistics&bcGroup=Department%20of%20Mathematics&bcItemType=programs) 
* [Biology](https://www.byui.edu/catalog/#/programs/V1ZfQQbhjb?bc=true&bcCurrent=Biology&bcGroup=Department%20of%20Biology&bcItemType=programs) - [Bioinformatics](https://www.byui.edu/catalog/#/programs/V1ZfQQbhjb/S1bp9GTkx?bc=true&bcCurrent=Bioinformatics&bcGroup=Department%20of%20Biology&bcItemType=programs)